\documentclass[UTF-8]{resume} \usepackage{multirow}
\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Blizzard Finnegan}
\address{{LinkedIn.com/in/BlizzardFinnegan} \\ {GitHub.com/BlizzardFinnegan}\hspace*{\fill} {+1(607)738-5933} \\ {Rochester, NY}}
\begin{document}
\hrule
Seeking co-op in firmware and software development. Available May - Dec. 2022

%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
	\begin{tabular}{ @{} >{\bfseries}r | @{\hspace{1ex}} l  }
		Languages & Java, C/C++, ZSH/BASH, VHDL\\
        \hline
		Software & \LaTeX, Git, MATLAB, Linux, ModelSim, MultiSim, Altera Quartus, Microsoft Excel\\
        \hline
        \multirow{2}{*}{Hardware} & Soldering iron, Oscilloscope, Digital multimeter, FPGAs, Signal/function generator, Arduino,\\
		&Scanning laser microscope, Scanning Electron Microscope
	\end{tabular}\\
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
	\vspace{-1.5em}
\item \textbf{Binary Search Tree}\hfill {February 2022} \\
    \emph{ Implement a Binary Search Tree, built in Java}
	\begin{itemize}
         \itemsep -5pt {}
	      \item Built based off of a given UML diagram
          \item Includes \verb|infixTraversal()|, \verb|binarySearch()|
          \item Easily sortable using \verb|Collections.sort()|
	\end{itemize}
\item \textbf{Arch Linux Livability Scripts} \hfill {April 2020 - Spring 2021}\\
	\emph{ZSH/BASH scripts built to improve stability of Arch Linux}
	\begin{itemize}
	    \itemsep -5pt {}
             \item Automated installation of ArchLinux
             \item Restricted update windows for greater stability
             \item Streamlined git repo updates
	\end{itemize}
\item \textbf{Encryption Key Generator} \hfill{March 2020}\\
	\emph{VHDL design to create and transmit an encryption key, given an 8-bit value}
       \begin{itemize}
           \itemsep -5pt {}
	        \item Using Altera Cyclone V FPGA
		    \item Extensive use of Quartus and Modelsim
            \item Implemented feedback from fellow students
	\end{itemize}
\item \textbf{Gesture-Controlled Motor System}\hfill {May 2019}\\
	\emph{C designed program to control a motor, given a gyroscopic input}
	\begin{itemize}
          \itemsep -5pt {}
	       \item Using ATMEL328 Arduino platform
	       \item Extensive use of \verb|I2C| protocol
           \item Used project management skills
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
	{\bf Rochester Institute of Technology}  \hfill {Aug. 2018 - Aug. 2024}\\
	B.S. in Computer Engineering Technology; GPA = 3.37/4.00
\end{rSection}


%----------------------------------------------------------------------------------------
        \begin{rSection}{Work Experience}
    	    \vspace{-1.6em}
        \item \textbf{Laboratory Technician} {- MACOM Technology Solutions} \hfill {June 2017 - Aug. 2018}\\
            \emph{Horseheads, NY}
            \begin{itemize}
                \itemsep -5pt {}
                \item Operated scanning laser microscope measurement system to assess failures and improve yield
                \item Compiled acquired data, and generated visualizations using Excel for ease of understanding
                \item Established and assisted in writing standard operating procedure for the scanning laser microscope
            \end{itemize}
        \item \textbf{Student Worker} {- Salsarita's Mexican Grill} \hfill {Sept. 2020 - Jan. 2021, Sept. 2021 - Current}\\
            \emph{Henrietta, NY}
            \begin{itemize}
                \itemsep -5pt {}
                \item Maintained safe work environment for staff and customers
                \item Regularly interfaced with customers for all parts of the order-handling process
                \item Managed inventory according to First In, First Out procedures
            \end{itemize}
        \end{rSection}
\end{document}
