\documentclass[UTF-8]{resume} \usepackage{multirow}
\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Blizzard Finnegan}
\address{{LinkedIn.com/in/BlizzardFinnegan} \\ {GitHub.com/BlizzardFinnegan}\hspace*{\fill} {+1(607)738-5933} \\ {Rochester, NY}}
\begin{document}
\hrule
Seeking co-op in firmware and software development. Available Jan. - Aug. 2023

%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
	\begin{tabular}{ @{} >{\bfseries}r | @{\hspace{1ex}} l  }
		Languages & VHDL, C/C++, Java, ZSH/BASH                                                                 \\
		\hline
		Software  & \LaTeX, Git, MATLAB, Linux, ModelSim, MultiSim, Altera Quartus, Microsoft Excel             \\
		\hline
		Hardware  & Soldering iron, Oscilloscope, Digital multimeter, FPGAs, Signal/function generator, Arduino \\
	\end{tabular}\\
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
	\vspace{-1.5em}
    \item \textbf{Freelance Server Management} \hfill {Aug. 2022 - Current}\\
    \emph{Management of an array of services, including public presence and documentation}
	\begin{itemize}
		\itemsep -6pt {}
		\item Ensures integration into pre-existing workflows with minimal disruption or downtime
        \item Management of Docker containers, Samba fileshare, hardware and software RAID arrays, and network stack
		\item Budget and acquire new hardware according to needs
        \item Implements user-friendly, intuitive tools with minimal learning curves
	\end{itemize}
	\item \textbf{Advent of Code 2021}\hfill {Dec. 2021 - Current}\\
	\emph{Series of coding challenges hosted online; written both in C++ and Java}
	\begin{itemize}
		\itemsep -6pt {}
		\item Manual implementation of Dijkstra's algorithm
		\item plaintext file parsing
		\item Extensive Stack, Queue, and ArrayList use
	\end{itemize}
	\item \textbf{Binary Search Tree}\hfill {February 2022} \\
	\emph{ Implement a Binary Search Tree, built in Java}
	\begin{itemize}
		\itemsep -6pt {}
		\item Built based off of a given UML diagram
		\item Includes \verb|infixTraversal()|, \verb|binarySearch()|
		\item Easily sortable using \verb|Collections.sort()|
	\end{itemize}
	\item \textbf{Encryption Key Generator} \hfill{March 2020}\\
	\emph{VHDL design to create and transmit an encryption key, given an 8-bit value}
	\begin{itemize}

		\itemsep -6pt {}
		\item Using Altera Cyclone V FPGA
		\item Extensive use of Quartus and Modelsim
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
	{\bf Rochester Institute of Technology}  \hfill {Aug. 2018 - June 2025}\\
	B.S. in Computer Engineering Technology; GPA = 3.37/4.00
\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
	\vspace{-1.6em}
    \item \textbf{Assistant Systems Administrator} {- RIT, Information \& Technology Services} \hfill {June 2022 - Dec. 2022}\\
	\emph{Henrietta, NY}
	\begin{itemize}
		\itemsep -6pt {}
		\item Maintained and repaired a wide range client devices
		\item Regularly interfaced with customers for identifying and resolving issues
		\item Maintain compatibility and security updates across several platforms
	\end{itemize}
	\item \textbf{Laboratory Technician} {- MACOM Technology Solutions} \hfill {June 2017 - Aug. 2018}\\
	\emph{Horseheads, NY}
	\begin{itemize}
		\itemsep -6pt {}
		\item Operated scanning laser microscope measurement system to assess failures and improve yield
		\item Compiled acquired data, and generated visualizations using Excel for ease of understanding
		\item Established and assisted in writing standard operating procedure for the scanning laser microscope
	\end{itemize}
\end{rSection}
\end{document}
