\documentclass[UTF-8]{resume} \usepackage{multirow}
\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Blizzard Finnegan}
\address{{LinkedIn.com/in/BlizzardFinnegan} \\ {GitHub.com/BlizzardFinnegan}\hspace*{\fill} {+1(607)738-5933} \\ {Rochester, NY}}
\begin{document}
\hrule
Seeking full-time position in software development and systems administration. Available Jan. - June 2023

%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
	\begin{tabular}{ @{} >{\bfseries}r | @{\hspace{1ex}} l  }
		Languages & Java, C/C++, ZSH/BASH                                                     \\
		\hline
		Software  & \LaTeX, Git, Docker, Wireguard, Linux (primarily Debian), Microsoft Excel \\
		\hline
		Hardware  & Cisco routers, M1 Mac, Dell systems, custom desktops
	\end{tabular}\\
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
	\vspace{-1.5em}
    \item \textbf{Freelance Server Management} \hfill {Aug. 2022 - Current}\\
    \emph{Management of an array of services, including public presence and documentation}
	\begin{itemize}
		\itemsep -6pt {}
		\item Ensures integration into pre-existing workflows with minimal disruption or downtime
        \item Management of Docker containers, Samba fileshare, hardware and software RAID arrays, and network stack
		\item Budget and acquire new hardware according to needs
        \item Implements user-friendly, intuitive tools with minimal learning curves
	\end{itemize}
	\item \textbf{Personal Network} \hfill{June 2022 - Current}\\
	\emph{Maintain personal cloud infrastructure, on personal devices}
	\begin{itemize}
		\itemsep -6pt {}
		\item Self-hosted reverse proxy, email, and DNS instances
		\item Built using custom desktop running Debian
		\item Admin access provided via a Wireguard tunnel
	\end{itemize}
	\item \textbf{Advent of Code 2021}\hfill {Dec. 2021 - Current}\\
	\emph{Series of coding challenges hosted online; written both in C++ and Java}
	\begin{itemize}
		\itemsep -6pt {}
		\item Manual implementation of Dijkstra's algorithm
		\item Plaintext file parsing
		\item Extensive Stack, Queue, and ArrayList use
	\end{itemize}
	\item \textbf{Binary Search Tree}\hfill {February 2022} \\
	\emph{ Implement a Binary Search Tree, built in Java}
	\begin{itemize}
		\itemsep -6pt {}
		\item Built based off of a given UML diagram
		\item Includes \verb|infixTraversal()|, \verb|binarySearch()|
		\item Easily sortable using \verb|Collections.sort()|
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
	{\bf Rochester Institute of Technology}  \hfill {Aug. 2018 - Aug. 2024}\\
	B.S. in Computer Engineering Technology; GPA = 3.37/4.00
\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
	\vspace{-1.6em}
	\item \textbf{Assistant Systems Administrator} {- RIT / Information \& Technology Services } \hfill {June 2022 - Dec. 2022}\\
	\emph{Henrietta, NY}
	\begin{itemize}
		\itemsep -5pt {}
		\item Assisted in management, installation, and maintenance of new personal and lab computers
		\item Regularly interfaced with Microsoft Active Directory and SCCM
		\item Assisted staff and students with basic IT needs
	\end{itemize}
	\item \textbf{Laboratory Technician} {- MACOM Technology Solutions} \hfill {June 2017 - Aug. 2018}\\
	\emph{Horseheads, NY}
	\begin{itemize}
		\itemsep -5pt {}
		\item Operated scanning laser microscope measurement system to assess failures and improve yield
		\item Compiled acquired data, and generated visualizations using Excel for ease of understanding
		\item Established and assisted in writing standard operating procedure for the scanning laser microscope
	\end{itemize}
\end{rSection}
\end{document}
